\bf Brother, Can You Spare a Manufacturing Job? White Voter Reactions to Deindustrialization

### 2021-11-30 rCode/Draft.Rmd
message

stargazer(regResultList$secondStageModelNetCA,
          regResultList$secondStageModelNetC,
          regResultList$secondStageModelWNetCA,
          regResultList$secondStageModelWNetC,
          se = list(
            regResultList$rseNetCA_2,
            regResultList$rseNetC_2,
            regResultList$rseWNetCA_2,
            regResultList$rseWNetC_2
          ),
          title = "Effect of Manufacturing Layoffs on Democratic Vote Share",
          dep.var.labels = "Change in Share (2012-2016)",
          omit.stat = c("rsq","ser"),
          keep = c("Manufacturing Layoffs", "White Manufacturing Layoffs", "Nonwhite Manufacturing Layoffs"),
          add.lines = list(
            c("Controls For White Share/Service Layoffs", "No", "Yes", "No", "Yes")
          ),
          digits = 2,
          type = "latex"
)

@@

stargazer(regResultList$secondStageModelNetC04A,
          regResultList$secondStageModelNetC04,
          regResultList$secondStageModelWNetC04A,
          regResultList$secondStageModelWNetC04,
          se = list(
            regResultList$rseNetC04A_2,
            regResultList$rseNetC04_2,
            regResultList$rseWNetC04A_2,
            regResultList$rseWNetC04_2
          ),
          title = "Effect of Manufacturing Layoffs on Democratic Vote Share (since 2004)",
          dep.var.labels = "Change in Share (2016-2012)",
          omit.stat = c("rsq","ser"),
          keep = c("Manufacturing Layoffs", "White Manufacturing Layoffs", "Nonwhite Manufacturing Layoffs"),
          add.lines = list(
            c("Controls For White Share/Service Layoffs", "No", "Yes", "No", "Yes")
          ),
          digits = 2,
          type = "latex"
)

>>>>

stargazer(regResultList$secondStageModelNetCA,
          regResultList$secondStageModelNetC,
          regResultList$secondStageModelWNetCA,
          regResultList$secondStageModelWNetC,
          se = list(
            regResultList$rseNetCA_2,
            regResultList$rseNetC_2,
            regResultList$rseWNetCA_2,
            regResultList$rseWNetC_2
          ),
          title = "Effect of Manufacturing Layoffs on Democratic Vote Share",
          dep.var.labels = "Change in Share (2012-2016)",
          omit.stat = c("rsq","ser"),
          keep = c("Manufacturing Layoffs", "White Manufacturing Layoffs", "Nonwhite Manufacturing Layoffs"),
          add.lines = list(
            c("Controls For White Share/Service Layoffs", "No", "Yes", "No", "Yes")
          ),
          digits = 2,
          header = F,
          type = "latex"
)

@@

stargazer(regResultList$secondStageModelNetC04A,
          regResultList$secondStageModelNetC04,
          regResultList$secondStageModelWNetC04A,
          regResultList$secondStageModelWNetC04,
          se = list(
            regResultList$rseNetC04A_2,
            regResultList$rseNetC04_2,
            regResultList$rseWNetC04A_2,
            regResultList$rseWNetC04_2
          ),
          title = "Effect of Manufacturing Layoffs on Democratic Vote Share (since 2004)",
          dep.var.labels = "Change in Share (2016-2012)",
          omit.stat = c("rsq","ser"),
          keep = c("Manufacturing Layoffs", "White Manufacturing Layoffs", "Nonwhite Manufacturing Layoffs"),
          add.lines = list(
            c("Controls For White Share/Service Layoffs", "No", "Yes", "No", "Yes")
          ),
          digits = 2,
          header = F,
          type = "latex"
)
